### 2023-07-12 polymorphism.tex
Updates from Overleaf

The case studies above demonstrate that the framework of the marked lambda calculus is suitable to support a variety of extensions to richer judgmental structures.
We hope that this spurs language designers to design marked variants of other calculi, following the
recipe we have demonstrated: starting with a gradual, bidirectional type system, by considering each
possible failure case, one may systematically derive the necessary error marks and marking rules.

We leave as future work the task of defining marked versions of even more elaborate bidirectional
type systems, e.g. \citet{dunfield2013complete}'s rather substantial formulation of implicit type
application in a bidirectional setting (which would have to handle, for example, the situation where
no implicit argument can be resolved).

% TODO cite gradual dependent types papers, etc.

>>>>

The case studies above demonstrate that the framework of the marked lambda calculus is suitable to support a variety of extensions to richer judgmental structures.
We hope that this spurs language designers to design marked variants of other calculi, following the
recipe we have demonstrated: starting with a gradual, bidirectional type system, by considering each
possible failure case, one may systematically derive the necessary error marks and marking rules.
The metatheorems, particularly totality, ensure that no rules or premises have been missed.

We leave as future work the task of defining marked versions of even more elaborate bidirectional
type systems, e.g. \citet{dunfield2013complete}'s rather substantial formulation of implicit type
application in a bidirectional setting (which would have to handle, for example, the situation where
no implicit argument can be resolved) or \citet{DBLP:phd/hal/LennonBertrand22}'s gradual bidirectional
variant of the dependently typed calculus of constructions.

% TODO cite gradual dependent types papers, etc.
% DBLP:phd/hal/LennonBertrand22
